Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-13 paper.tex
Updated glossary

\item \textit{Metabolites} - Metabolites are the intermediates and products of metabolism. The term metabolite is
    usually restricted to small molecules (chemical compounds).
\item \textit{Proteochemometric modeling} - combining data mining for chemical compounds (ligands) and proteins
    within the same machine learning framework.

@@

\item \textit{Regulation authorities} - In the US the Food and Drug Administration (FDA) is responsible for

>>>>

@@

\item \textit{Regulatory authorities} - In the US the Food and Drug Administration (FDA) is responsible for
